### 2014-11-04 paper/main.tex
added code to produce good/poor figure
slight update of text and figures for good-poor illustration

\pagestyle{myheadings}
%% ** EDIT HERE **
\usepackage{enumerate}
\usepackage{multirow} 
\usepackage{url}
\usepackage{xr} %for cross-referencing
%% ** EDIT HERE **
%% PLEASE INCLUDE ALL MACROS BELOW
\newtheorem{algorithm}{Algorithm}
\newtheorem{proposition}{Proposition}
\newtheorem{restateproposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{result}{Result}
\newtheorem{note}{Note}
\newtheorem{definition}{Definition}

@@

Many tools have been developed for this problem \cite{}, and several are widely used.
Here we argue that these existing tools have sub-optimal features that can be improved on, at least in some circumstances.
In particular we argue that existing tools i) fail to take proper account of variations in the measurement precision of different effects;
ii) make, implicitly, unrealistic assumptions about the distribution of the non-zero effects. We provide methods
to address these problems, implemented in an R package {\tt ashr} (short for ``Adaptive Shrinkage") and demonstrate that these methods can lead to a substantial reduction in estimated FDRs (or, equivalently,
a substantial increase in the number of discoveries at a given FDR).

@@

Given that shrinkage estimation is widely recognized as a powerful tool, there are surprisingly few software packages for performing the simplest type of shrinkage estimation considered here. (There are more packages for the more complex setting of covariance estimation, where shrinkage is perhaps still more important.)
The only package we have found that provides anything similar
to the functionality provided here is \mixfdr \cite{muralidharan2010empirical}. Compared with \mixfdr, the key features of ashr are that it
i) focuses on allowing for variation in the standard deviation of each observation; ii) constrains the underlying density to be unimodal (and possibly symmetric).
NOTE: should emphasize these differences in the examples.

@@

Possibly show two situations in figure - a high signal and low signal situation?

@@

 There are two issues with existing approaches to FDR estimation and control that I would like to address here. 
 The first is that they do not take proper account of differences in measurement precision across units (i.e. differences in $\shat_j$). 
 The second is that the Zero Assumption, although initially appealing as a ``conservative" assumption,
  is often an unrealistic and unnecessarily conservative assumption. As we shall see, both factors can cause the FDR to be overestimated.

@@

To give a concrete example, we performed a simple simulation in which half the observations have
reasonably good precision ($s_j = 1$) and half the observations have very poor precision ($s_j=10$). In both cases,
we assume that half the effects are null ($\beta_j=0$)
and the other half are normally distributed with standard deviation 1 ($\beta_j \sim N(0,1)$). 
That is, we simulate $\beta_j$ from a mixture 
\begin{equation}
p(\beta) = 0.5 \delta_0(\beta) + 0.5 N(\beta; 0,1)
\end{equation}
where $\delta_0(\cdot)$ denotes a point mass at 0.

\begin{figure}
\center \includegraphics[width=6.5in]{Rcode/figures/GOODPOOReg_hist.pdf}
\caption{Illustration of the way that high-noise observations can contaminate signal from low-noise observations.} \label{fig:GOODPOOR}
\end{figure}

Note that the problem could be reduced by discarding measurements that are too noisy. However,
note limitation of this.

To illustrate the second issue, it is helpful to go back from the $p$ values in Figure \ref{}

Illustration (Figure).

>>>>

\pagestyle{myheadings}
%% ** EDIT HERE **
\usepackage{enumerate}
\usepackage{subfig}
\usepackage{multirow} 
\usepackage{url}
\usepackage{xr} %for cross-referencing
%% ** EDIT HERE **
%% PLEASE INCLUDE ALL MACROS BELOW
\newtheorem{algorithm}{Algorithm}
\newtheorem{proposition}{Proposition}
\newtheorem{restateproposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{result}{Result}
\newtheorem{note}{Note}
\newtheorem{definition}{Definition}

@@

Many tools have been developed for this problem \cite{}, and several are widely used.
Here we argue that these existing tools have sub-optimal features that can be improved on, at least in some circumstances.
In particular we argue that existing tools i) fail to take proper account of variations in the measurement precision of different effects;
ii) make, implicitly, unrealistic assumptions about the distribution of the non-zero effects. We provide methods
to address these problems, implemented in an R package \ashr (short for ``Adaptive Shrinkage") and demonstrate that these methods can lead to a substantial reduction in estimated FDRs (or, equivalently,
a substantial increase in the number of discoveries at a given FDR).

@@

Given that shrinkage estimation is widely recognized as a powerful tool, there are surprisingly few software packages for performing the simplest type of shrinkage estimation considered here. (There are more packages for the more complex setting of covariance estimation, where shrinkage is perhaps still more important.)
The only package we have found that provides anything similar
to the functionality provided here is \mixfdr \cite{muralidharan2010empirical}. Compared with \mixfdr, the key features of \ashr are that it
i) focuses on allowing for variation in the standard deviation of each observation; ii) constrains the underlying density to be unimodal (and possibly symmetric).
NOTE: should emphasize these differences in the examples.

@@

@@

 There are two issues with existing approaches to FDR estimation and control that I would like to address here. 
 The first is that they may do not take proper account of differences in measurement precision across units (i.e. differences in $\shat_j$). 
 The second is that the Zero Assumption, although initially appealing as a ``conservative" assumption,
  is often an unrealistic and unnecessarily conservative assumption. As we shall see, both factors can cause the FDR to be overestimated.

@@

To give a concrete example, we performed a simple simulation in which half the observations have
reasonably good precision (standard error $s_j = 1$) and half the observations have very poor precision ($s_j=10$). In both cases,
we assume that half the effects are null ($\beta_j=0$)
and the other half are normally distributed with standard deviation 1 ($\beta_j \sim N(0,1)$). 
That is, we simulate $\beta_j$ from a mixture 
\begin{equation}
p(\beta) = 0.5 \delta_0(\beta) + 0.5 N(\beta; 0,1)
\end{equation}
where $\delta_0(\cdot)$ denotes a point mass at 0.

Figure \ref{fig:goodpoor-hist} shows the distribution of the resulting $p$ values for the good-precision and poor-precision measurements, as
well as the combined distribution. As expected, the poor-precision measurements lead to almost-uniform $p$ values, and when combined
with the good-precision measurements they dilute the overall signal in the $p$ values (e.g. they reduce the density of $p$ values near 0).
This is reflected in the results of FDR methods like $\qvalue$ and $\locfdr$, which work with the $p$ values and $Z$ scores respectively:
the estimated error rates ($q$-values, or lfdr values) for the good-precision observations increase when the low-precision observations are included in the analysis
(Figure \ref{fig:goodpoor-scatter}). In contrast, the methods described here ($\ashr$) take account of the precision of each measurement, and so
the estimated error rates for the good-precision observations are unaffected by including the low-precision observations in the analysis.
(A key assumption of this simulation is that the distribution of the effects $\beta$ is the same for the good-precision and poor-precision measurements;
we return to discuss this assumption in more detail in section \ref{xx})

\begin{figure}
\centering
\subfloat[][Histograms of $p$ values for good-precision, poor-precision, and combined observations]{
\includegraphics[width=6.5in]{Rcode/figures/GOODPOOReg_hist.pdf} 
    \label{fig:goodpoor-hist}
} \\
\subfloat[][Comparison of results of different methods applied to good-precision observations only ($x$ axis) and combined data ($y$ axis). Each point shows the estimated error rate ($q$ value, lfdr, or lfsr) for a good-precision observation under the two different analyses.]{
\includegraphics[width=6.5in]{Rcode/figures/GOODPOOReg_scatter.pdf}
    \label{fig:goodpoor-scatter}
}
\caption{Simulated illustration how poor-precision observations can contaminate signal from good-precision observations. The top panel (a) illustrates that when 
$p$ values from good-precision observations (left) and from poor-precision observations (center) are combined (right), they produce
a distribution of $p$ values with less overall signal - and so, by conventional methods, will give a higher estimated FDR at any given threshold.
The bottom panel (b) illustrates this behaviour directly for the methods \qvalue and \locfdr: the $q$-values from \qvalue and the lfdr estimates from \locfdr are higher when applied to all data than when applied to good-precision observations only. In contrast the methods described here (\ashr) produce effectively the same results (here, the lfsr) in the good-precision and combined data analyses.} \label{fig:goodpoor}
\end{figure}
